Precise predictions for same-sign W-bosons scattering at the LHC

### 2017-12-12 Draft/article.tex
new changes on the draft (very long train ride thanks to DB...)
added EPJC template

%% Main-Version Draft
\documentclass[11pt,epsf]{article}
%% -------------------------------
%% |          Packages           |
%% -------------------------------
 \usepackage{amsmath}
 \usepackage{graphicx}
 \usepackage[merge,numbers,compress]{natbib}
 \usepackage[T1]{fontenc}
 \usepackage{booktabs}
 \usepackage{xcolor} 
 \usepackage{xspace}
 \usepackage{dcolumn}
 \usepackage{hyperref}
 \usepackage{caption}
 \usepackage{tabularx}
 \usepackage{lmodern}
 \usepackage
 [subrefformat=parens,position=top,skip=-15pt,margin=15pt,justification=justified,singlelinecheck=false]
 {subcaption}

\setlength{\evensidemargin}{0cm}
\setlength{\oddsidemargin}{0cm}
\setlength{\topmargin}{0.00cm}
\setlength{\textwidth}{16.0cm}
\setlength{\textheight}{22.55cm}
\setlength{\headheight}{0cm}
\setlength{\headsep}{0cm}
\setlength{\voffset}{0cm}
\setlength{\paperheight}{27cm}

\renewcommand{\topfraction}{0.8}
\renewcommand{\bottomfraction}{0.5}
\renewcommand{\textfraction}{0.2}
\renewcommand{\floatpagefraction}{0.7}

@@

%% ---------------------------------
%% | ToDo Marker - only for draft! |
%% ---------------------------------
% Remove this section for final version!
\setlength{\marginparwidth}{20mm}

@@

\input{macros}

\begin{document}

\title{\hfill ~\\[-30mm]
\phantom{h} \hfill\mbox{\small DESY PREPRINT } \\
\vspace{-10mm}
\phantom{h} \hfill\mbox{\small KIT PREPRINT } \\
\vspace{-10mm}
\phantom{h} \hfill\mbox{\small NIKHEF PREPRINT } \\
\vspace{-10mm}
\phantom{h} \hfill\mbox{\small ZURICH PREPRINT }
\\[1cm]
% \vspace{13mm}   
\textbf{Precise predictions for same sign W-bosons scattering at the LHC}}

\date{}
\author{
Benedikt Biedermann$^{1\,}$,
Simon Brass$^{2\,}$,
Ansgar Denner$^{1\,}$,
Stefan Dittmaier$^{3\,}$,
Michele Grossi$^{4,5\,}$, \\
Alexander Karlberg$^{6\,}$, 
Mathieu Pellen$^{1\,}$\footnote{E-mail:
  \texttt{mpellen@physik.uni-wuerzburg.de}},
Giovanni  Pelliccioli$^{7\,}$,
Michael Rauch$^{8\,}$,
J\"urgen Reuter$^{9\,}$, \\
Vincent Rothe$^{9\,}$, 
Christopher Schwan$^{3\,}$,
Pascal Stienemeier$^{9\,}$,
Marco Zaro$^{10\,}$\footnote{E-mail:
  \texttt{m.zaro@nikhef.nl}}.
\\[9mm]
{\small\it
$^1$Universit\"at W\"urzburg, %
        Institut f\"ur Theoretische Physik und Astrophysik,} \\ %
{\small\it Emil-Hilb-Weg 22, \linebreak %
        97074 W\"urzburg, %
        Germany}\\[3mm]
        %
{\small\it
$^2$Universit\"at Siegen, Department Physik,} \\ %
{\small\it Walter-Flex-Str.3, \linebreak %
        57068 Siegen, Germany}\\[3mm]
        %
$^3${\small\it
Albert-Ludwigs-Universit\"at Freiburg, Physikalisches Institut,} \\ %
{\small\it Hermann-Herder-Str.\ 3, \linebreak %
         79104 Freiburg, Germany}\\[3mm]
        %
{\small\it
$^4$Universit\'a di Pavia, Dipartimento di Fisica and INFN, Sezione di Pavia } \\ %
{\small\it Via A. Bassi 6, \linebreak %
        27100 Pavia, %
        Italy}\\[3mm]
%        
{\small\it
$^{5}$IBM Italia s.p.a.} \\ %
{\small\it Circonvallazione Idroscalo , \linebreak %
        20090 Segrate (MI), %
        Italy}\\[3mm]
        %
{\small\it
$^6$Department of Physics, University of Z\"urich,} \\ %
{\small\it CH-8057
Z\"urich, Switzerland}\\[3mm]
        %
$^7${\small\it
Universit\`a di Torino, Dipartimento di Fisica and INFN, Sezione di Torino } \\ %
{\small\it Via P. Giuria 1, \linebreak %
        10125 Torino, %
        Italy}\\[3mm]
        %
{\small\it
$^8$Institute for Theoretical Physics, Karlsruhe Institute of
Technology (KIT),} \\ %
{\small\it Karlsruhe, Germany}\\[3mm]
        %
{\small\it
$^9$DESY Theory Group,} \\ %
{\small\it Notkestr. 85, \linebreak %
        D-22607 Hamburg, Germany}\\[3mm]
        %
{\small\it
$^{10}$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]        
        }

@@

\newpage

@@

\subsection{Scan}

@@

\subsection{ScanNLO}

>>>>

%% Main-Version Draft
\documentclass[twocolumn,epjc3]{svjour3} % use the EPJC template, two columns
%%\documentclass[epjc3]{svjour3} % use the EPJC template, one column
\smartqed  % flush right qed marks, e.g. at end of proof
%% -------------------------------
%% |          Packages           |
%% -------------------------------
 \usepackage{amsmath}
 \usepackage{graphicx}
 \usepackage[merge,numbers,compress]{natbib}
 \usepackage[T1]{fontenc}
 \usepackage{booktabs}
 \usepackage{xcolor} 
 \usepackage{xspace}
 \usepackage{dcolumn}
 \usepackage{hyperref}
 \usepackage{caption}
 \usepackage{tabularx}
 \usepackage{lmodern}
% \usepackage
% [subrefformat=parens,position=top,skip=-15pt,margin=15pt,justification=justified,singlelinecheck=false]
% {subcaption}

%\setlength{\evensidemargin}{0cm}
%\setlength{\oddsidemargin}{0cm}
%\setlength{\topmargin}{0.00cm}
%\setlength{\textwidth}{16.0cm}
%\setlength{\textheight}{22.55cm}
%\setlength{\headheight}{0cm}
%\setlength{\headsep}{0cm}
%\setlength{\voffset}{0cm}
%\setlength{\paperheight}{27cm}

%\renewcommand{\topfraction}{0.8}
%\renewcommand{\bottomfraction}{0.5}
%\renewcommand{\textfraction}{0.2}
%\renewcommand{\floatpagefraction}{0.7}

@@

%% ---------------------------------
%% | ToDo Marker - only for draft! |
%% ---------------------------------
% Remove this section for final version!
%\setlength{\marginparwidth}{20mm}

@@

\input{macros}
%
\journalname{PREPRINT NUMBERS HERE}
%
\begin{document}

\title{Precise predictions for same-sign W-bosons scattering at the LHC}

\author{Benedikt Biedermann\thanksref{wurz}
\and
Simon Brass\thanksref{sieg}
\and
Ansgar Denner\thanksref{wurz}
\and
Stefan Dittmaier\thanksref{frei}
\and
Michele Grossi\thanksref{pavia,ibm}
\and
Alexander Karlberg\thanksref{uzh} 
\and
Mathieu Pellen\thanksref{wurz,e1}
\and
Giovanni  Pelliccioli\thanksref{unito}
\and
Michael Rauch\thanksref{kit}
\and
J\"urgen Reuter\thanksref{desy}
\and
Vincent Rothe\thanksref{desy} 
\and
Christopher Schwan\thanksref{frei}
\and
Pascal Stienemeier\thanksref{desy}
\and
Marco Zaro\thanksref{nikh,e2}
}

\thankstext{e1}{e-mail: mpellen@physik.uni-wuerzburg.de}
\thankstext{e2}{e-mail: m.zaro@nikhef.nl}

\institute{Universit\"at W\"urzburg, %
Institut f\"ur Theoretische Physik und Astrophysik,  %
Emil-Hilb-Weg 22, %
97074 W\"urzburg, %
Germany\label{wurz} 
\and
Universit\"at Siegen, Department Physik, %
 Walter-Flex-Str.3, %
57068 Siegen, Germany\label{sieg}
\and
Albert-Ludwigs-Universit\"at Freiburg, Physikalisches Institut, %
 Hermann-Herder-Str.\ 3, %
79104 Freiburg, Germany\label{frei}
\and
Universit\'a di Pavia, Dipartimento di Fisica and INFN, Sezione di Pavia, %
Via A. Bassi 6, %
27100 Pavia, %
Italy\label{pavia}
\and
IBM Italia s.p.a. %
Circonvallazione Idroscalo , %
20090 Segrate (MI), %
Italy\label{ibm}
\and
Department of Physics, University of Z\"urich, %
CH-8057 Z\"urich, 
Switzerland\label{uzh}
\and
Universit\`a di Torino, Dipartimento di Fisica and INFN, Sezione di Torino, %
Via P. Giuria 1, %
10125 Torino, %
Italy\label{unito}
\and
Institute for Theoretical Physics, Karlsruhe Institute of
Technology (KIT), %
Karlsruhe, 
Germany\label{kit}
\and
DESY Theory Group, %
Notkestr. 85, %
D-22607 Hamburg, 
Germany\label{desy}
\and
Nikhef,
Science Park 105,
1098XG Amsterdam,
The Netherlancs\label{nikh}
}

@@

@@

\subsection{Three contributions}

\input{contributions}

\subsection{Inclusive comparison}

@@

\subsection{Inclusive comparision}

### 2017-12-12 Draft/description.tex
added EPJC template

In the comparison, the following codes are used:

\begin{itemize}
 \item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator
and matrix elements taken from several sources: Born matrix elements are
adapted from the program {\sc Lusifer} \cite{Dittmaier:2002ap} for the partonic
processes, real matrix elements are written by Marina Billoni, and virtual
matrix elements by Stefan Dittmaier.
One loop integrals are evaluated using the {\sc Collier} library
\cite{Denner:2014gla,Denner:2016kdg}.

@@

% The complete comparison of the codes will be published in a separate work. Here, we present some preliminary results obtained at LO ($\mathcal O (\alpha^6)$) and including
NLO QCD corrections at fixed-order $\mathcal O (\alpha^6\alpha_s)$, for the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
In Tab.~\ref{tab:wg1_codes} the details of the various codes are reported. In particular, it is specified whether
\begin{itemize}
    \item all $s$- and $t/u$-channel diagrams that lead to the considered final state are included;
    \item interferences between diagrams are included at LO;
    \item diagrams which do not feature two resonant vector bosons are included;
    \item the so-called non-factorisable (NF) QCD corrections, that is the corrections where (real or virtual) gluons are exchanged between different quark lines,
        are included;
    \item EW corrections to the $\mathcal O (\alpha^5\alpha_s)$ interference are included. These corrections are of the same order as the NLO QCD corrections to
        the  $\mathcal O (\alpha^6$) term.
\end{itemize}
%
\begin{table}
    \footnotesize
    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
        Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  & NLO &  NF QCD  &  EW corr. to $\mathcal O(\alpha^5\alpha_s)$  \\
        \hline
        \hline
        {\sc Bonsay}  &  $t/u$  &  No  &  Yes, virt. No  & Yes & No  &  No  \\
        {\sc POWHEG}  &  $t/u$  &  No  &  Yes  &  Yes & No  &  No  \\
        {\sc MG5\_aMC}  &  Yes  &  Yes  &  No virt.  & Yes & No  &  No \\
        {\sc MoCaNLO+Recola}  &  Yes  &  Yes  &  Yes  &  Yes & Yes  &  Yes  \\
        {\sc PHANTOM}  &  Yes  &  Yes  &  Yes  & No & - & - \\  
        {\sc VBFNLO}  &  Yes  &  No  &  Yes  &  Yes & No  &  No  \\
        {\sc Whizard}  &  Yes  &  Yes  &  Yes  & No & - & - \\  
    \end{tabularx}
    \caption{\label{tab:wg1_codes} Summary of the different properties of the codes employed in the comparison.}
\end{table}
%

>>>>

\begin{table*}[ht!]
    \footnotesize
    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
        Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  & NLO &  NF QCD  &  EW corr. to $\mathcal O(\alpha^5\alpha_s)$  \\
        \hline
        \hline
        {\sc Bonsay}        &  $t/u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
        {\sc POWHEG}        &  $t/u$    &  No       &  Yes              &  Yes   & No       &  No  \\
        {\sc MG5\_aMC}      &  Yes      &  Yes      &  Yes              &  Yes   & No virt. &  No \\
        {\sc MoCaNLO+Recola}&  Yes      &  Yes      &  Yes              &  Yes   & Yes      &  Yes  \\
        {\sc PHANTOM}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\  
        {\sc VBFNLO}        &  Yes      &  No       &  Yes              &  Yes   & No       &  No  \\
        {\sc Whizard}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\  
    \end{tabularx}
    \caption{\label{tab:wg1_codes} Summary of the different properties of the codes employed in the comparison.}
\end{table*}

In the comparison, the following codes are used: 
\begin{itemize}
 \item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator
and matrix elements taken from several sources: Born matrix elements are
adapted from the program {\sc Lusifer} \cite{Dittmaier:2002ap} for the partonic
processes, real matrix elements are written by Marina Billoni, and virtual
matrix elements by Stefan Dittmaier.
One loop integrals are evaluated using the {\sc Collier} library
\cite{Denner:2014gla,Denner:2016kdg}.

@@

% The complete comparison of the codes will be published in a separate work. Here, we present some preliminary results obtained at LO ($\mathcal O (\alpha^6)$) and including
NLO QCD corrections at fixed-order $\mathcal O (\alpha^6\alpha_s)$, for the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
In Tab.~\ref{tab:wg1_codes} the details of the various codes are reported. In particular, it is specified whether
\begin{itemize}
    \item all $s$- and $t/u$-channel diagrams that lead to the considered final state are included;
    \item interferences between diagrams are included at LO;
    \item diagrams which do not feature two resonant vector bosons are included;
    \item the so-called non-factorisable (NF) QCD corrections, that is the corrections where (real or virtual) gluons are exchanged between different quark lines,
        are included;
    \item EW corrections to the $\mathcal O (\alpha^5\alpha_s)$ interference are included. These corrections are of the same order as the NLO QCD corrections to
        the  $\mathcal O (\alpha^6$) term.
\end{itemize}
%
%
